---
title: "Industrial Statistics (QE final assignment)"
author: 'ID: 204166524'
date: "19.7.2020"
output:
  html_document: default
  pdf_document: default
---

# Libraries
```{r}
suppressPackageStartupMessages(library(IQCC)) # Don't show me the startup messages
suppressPackageStartupMessages(library(FrF2))
```

# Question 1

## 1.1
```{r, echo=TRUE}
seed <- 204166524

set.seed(seed)
x <- rnorm(100)
```
## 1.2
The first observation in the data is: `r x[1]`

## 1.3
```{r}
mu <- mean(x)
USL <- 2
LSL <- -2
range1 <- max(x)- min(x)
d2 <- d2(length(x))
sigma <- (range1)/d2
Cpu <- (USL-mu)/(3*sigma)
Cpl <- (mu-LSL)/(3*sigma)
Cpk <- min(c(Cpu,Cpl))
```
The $C_{pk}$ value is: $C_{pk} =$ `r Cpk` 


## 1.4
```{r, echo=TRUE}
Cp <- ((USL-LSL)/(6*sigma))
n <- 100
alpha <- 0.05
L_Limit <- Cp*sqrt(qchisq ( ( (alpha)/2) ,(n-1) )/ (n-1))
U_Limit <- Cp*sqrt(qchisq ( ( (1-(alpha) )/ 2), (n-1))/ (n-1))
```
The interval estimation for $C_{p}$ is: 

$C_{p} \in \big[$ `r L_Limit` , `r U_Limit` $\big]$
# Question 2

## 2.1
```{r, echo=TRUE}
set.seed(seed)
periods.1 <- 100
phase.1 <- rnorm(periods.1)
mu0 <- mean(phase.1)
sd0 <- sd(phase.1)
```

## 2.2
```{r, echo=TRUE}
L <- 3
CL <- mu0
n <- length(periods.1)
UCL <- CL+L*sd0/sqrt(1)
LCL <- CL-L*sd0/sqrt(1)
```
The control limits are:

LCL : `r LCL`

UCL : `r UCL`

## 2.3

From the code above, the actual expectancy is 0 and the standard deviation is 1.
It can be inferred from the forth line of the attached code,
when we sample 100 random numbers from standard normal distribution (these are the default values of the function)

## 2.4

```{r, echo=TRUE}
set.seed(seed)
periods.2 <- 1e4
phase.2 <- rnorm(periods.2) # generate another 10,000 samples
```
## 2.5

```{r, echo=TRUE}
alpha <- 2700/ 1e6 # l=3, meaning 2700 PPM 
ARL0 <- 1/alpha

l <- c(0)
gap <- 0
for (i in 1:length(phase.2)){
  gap <- gap+1
  if (phase.2[i] > UCL || phase.2[i] < LCL) {
    l<-c(l,gap) 
    gap <- 0 
  }
}

l <- l[-c(1)] # remove the first elemnt of the list 
simulated_ARL0 <- mean(l)
```
Simulated_ARL0 : `r simulated_ARL0`

We can see that the ARL0 is smaller in the simulation I made, which means more false alerms are produced.

# Question 3

## 3.1
```{r, echo=TRUE}
set.seed(seed)
periods <- 100
p <- 5
alpha <- 0.1
alpha_star <- 1 - (1 - alpha)^(1/p)
L <- -qnorm(alpha/2)
data <- matrix(rnorm(periods*p), nrow = periods)
Phase1_mat<- data[1:50,] # first 50 rows of the data for phase 1




CL3 <-  empty_vec <- rep(NA, 5)
SD3 <- rep(NA, 5)
UCL3 <- rep(NA, 5)
LCL3 <- rep(NA, 5)

for (i in 1:5){
  temp_cl3 <- mean(Phase1_mat[1:50,i])
  temp_sd3 <- sd(Phase1_mat[1:50,i])
  
  CL3[i] <- temp_cl3
  SD3[i] <- temp_sd3
  
  
  #### choose 1 option 
  UCL3[i] <- quantile(Phase1_mat[1:50,i],1-alpha_star/2)
  LCL3[i] <- quantile(Phase1_mat[1:50,i],alpha_star/2)
  
  # UCL3[i] <- CL3[i]+L*SD3[i]/sqrt(1) # emprical distbition
  # LCL3[i] <- CL3[i]-L*SD3[i]/sqrt(1) # emprical distbition
}
for (p in 1:5){
  temp_paste <- paste("Variable ", p, " LCL : ", LCL3[p], "UCL :", UCL3[p] )
  print(temp_paste) # check why not printing ~!!!!
}
```  
## 3.2
  
```{r, echo=TRUE}
x <- Phase1_mat
n <- nrow(Phase1_mat)
mu0 <- CL3
sigma0 <- cov(Phase1_mat) # cov matrix
sigma0.inv <- solve(sigma0) # inverse cov matrix
valid <- sigma0 %*% sigma0.inv # sanity check



t_squre <- n * (x-mu0) %*% sigma0.inv %*% t((x-mu0))
UCL_3.2 <- qchisq ( ( (1-(alpha) )), (5))

```

The inverse covariance matrix is:
``` {r}
prmatrix(sigma0.inv, rowlab =, collab =,
         quote = TRUE, right = FALSE, na.print = NULL)
```

Hotteling’s UCL:  `r UCL_3.2`

When alpha is set to $10$%, $ARL_{0} = \frac{1}{\alpha} = \frac{1}{0.1} = 10$

## 3.3
```{r, echo=TRUE}
Phase2_vec_2 <- data[51:100,2]
n <- nrow(Phase2_vec_2)
sd_3.2 <- SD3[2] 

Rule1 <- function(x, sd){
     result <- FALSE
     if( sum(x > CL3[2]+3*sd)>0){
       result <- TRUE}
     if( sum(x < CL3[2]-3*sd)>0){
       result <- TRUE}
     return(result)
    }

Rule2 <- function(x, sd){
    result <- FALSE
      if( (sum(x > CL3[2]+2*sd && x < CL3[2]+3*sd )) > 1) # although the "and" is unnecessary because the first rule is always checked first
        {result = TRUE}
      if( (sum(x < CL3[2]-2*sd && x > CL3[2]-3*sd ))> 1 ) # although the "and" is unnecessary because the first rule is always checked first
        {result = TRUE}
      return(result)
     }

Rule3 <- function(x, sd){
    result <- FALSE
     if( (sum(x > CL3[2]+ 1*sd))>=4)
       {result = TRUE}
     if( (sum(x < CL3[2]- 1*sd))>=4)
       {result = TRUE}
     return(result)
     }


Rule4 <- function(x,sd){
    result <- FALSE
     if( (sum(x > CL3[2])) >=8)
       {result <- TRUE}
     if( (sum(x < -CL3[2]))>=8)
       {result <- TRUE}
     return(result)
}


Rule5 <- function(x,sd){
    increasing <- 0
    decreasing <- 0
    result <- FALSE
     for (i in 1:5){
       if(x[i] < x[i+1]) {
         increasing <- increasing + 1 
       }
     if(x[i] > x[i+1]) {
         decreasing <- decreasing + 1 
       }
     }
    if (increasing == 5 || decreasing ==5)
    {result <- TRUE}
return (result) 
}

Rule6 <- function(x,sd){
    result <- FALSE
     if( (sum(x < CL3[2] + 1*sd && x > CL3[2] - 1*sd)) >=15)
       {result <- TRUE}
     return(result)
}

Rule7 <- function(x,sd){
  x <- x/abs(x)
    result <- FALSE
    count <- 0
    for (i in 1:13)
    {
      if (x[i] * x[i+1] == -1)
      {count <- count + 1}
    }
    if (count == 13)
        {result <- TRUE}
     return(result)
}

Rule8 <- function(x, sd){
    result <- FALSE
     if( (sum(x > CL3[2]+ 1*sd))>=8)
       {result = TRUE}
     if( (sum(x < CL3[2]- 1*sd))>=8)
       {result = TRUE}
     return(result)
     }

sum <- 0
for(i in 1:50){
    x<-c(Phase2_vec_2[i])
    if(Rule1(x,sd_3.2)) {
      print("rule 1")
      sum <- sum+1 }
    
    if (i >= 3) {
    x<-c(Phase2_vec_2[i],Phase2_vec_2[i-1],Phase2_vec_2[i-2])
      if(Rule2(x,sd_3.2)==TRUE) {
        print("rule 2")
        sum <- sum+1 }}
    
    if (i >= 5) {
    x<-c(Phase2_vec_2[i],Phase2_vec_2[i-1],Phase2_vec_2[i-2],Phase2_vec_2[i-3],Phase2_vec_2[i-4])
      if(Rule3(x,sd_3.2)==TRUE) {
        print("rule 3")
        sum <- sum+1 }}
    
    if (i >= 8) {
    x<-c(Phase2_vec_2[i],Phase2_vec_2[i-1],Phase2_vec_2[i-2],Phase2_vec_2[i-3],Phase2_vec_2[i-4],Phase2_vec_2[i-5],Phase2_vec_2[i-6],Phase2_vec_2[i-7])
      if(Rule4(x,sd_3.2)==TRUE) {
        print("rule 4")
          sum <- sum+1 }}
    
    if (i >= 6) {
    x<-c(Phase2_vec_2[i],Phase2_vec_2[i-1],Phase2_vec_2[i-2],Phase2_vec_2[i-3],Phase2_vec_2[i-4],Phase2_vec_2[i-5])
      if(Rule5(x,sd_3.2)==TRUE) {
        print("rule 5")
          sum <- sum+1 }}
    
    if (i >= 15) {
    x<-c(Phase2_vec_2[i],Phase2_vec_2[i-1],Phase2_vec_2[i-2],Phase2_vec_2[i-3],Phase2_vec_2[i-4],Phase2_vec_2[i-5],Phase2_vec_2[i-6],Phase2_vec_2[i-7],Phase2_vec_2[i-8],Phase2_vec_2[i-9],Phase2_vec_2[i-10],Phase2_vec_2[i-11],Phase2_vec_2[i-12],Phase2_vec_2[i-13],Phase2_vec_2[i-14])
      if(Rule6(x,sd_3.2)==TRUE) {
        print("rule 6")
          sum <- sum+1 }}
    
    if (i >= 14) {
    x<-c(Phase2_vec_2[i],Phase2_vec_2[i-1],Phase2_vec_2[i-2],Phase2_vec_2[i-3],Phase2_vec_2[i-4],Phase2_vec_2[i-5],Phase2_vec_2[i-6],Phase2_vec_2[i-7],Phase2_vec_2[i-8],Phase2_vec_2[i-9],Phase2_vec_2[i-10],Phase2_vec_2[i-11],Phase2_vec_2[i-12],Phase2_vec_2[i-13])
      if(Rule7(x,sd_3.2)==TRUE) {
        print("rule 7")
          sum <- sum+1 }}
    
        if (i >= 8) {
    x<-c(Phase2_vec_2[i],Phase2_vec_2[i-1],Phase2_vec_2[i-2],Phase2_vec_2[i-3],Phase2_vec_2[i-4],Phase2_vec_2[i-5],Phase2_vec_2[i-6],Phase2_vec_2[i-7])
      if(Rule8(x,sd_3.2)==TRUE) {
          print("rule 8")
          sum <- sum+1 }}
    
    if (sum > 0){
      print(i)
      break}
}

```

In the time period between days 51-100 there was no alarm. I've tried generating data using different seeds to make sure that the WECO detectors I have implemented work correctly. If I had an alarm, it would have been a false alarm. the reason for that is that I know the real distribution of the data because I have generated it and I know the mean and the standard deviation hasn't changed, hence it could only be false alarm.

# Question 4

## 4.1
```{r, echo=TRUE}
design <- FrF2(nruns = 8, nfactors = 5)
```

## 4.2
```{r}
print("The alising structure of this planning is:")
print("Aliases of treatment effects that are aliased with block main effects:")
design.info(design)$aliased[2] # print !!!
print("Aliases of Two-Factor Interactions:")
design.info(design)$aliased[3]

```
# Question 5

## 5.1
```{r, echo=TRUE}
set.seed(seed)
n <- 100
p <- 10
X <- matrix(rnorm(n*p), nrow = n)
mod <- 2^15
beta <- rep((seed %/% mod)/mod, p)
y <- exp(X %*% beta)
```

## 5.2.

The name of the model which we generated the data from is: Accelerated Life model

## 5.3
The real effects are:

```{r, echo=TRUE}

for (i in 1:10)
{
  temp<- paste("beta", i,":", beta[i])
  (print(temp))
}

```

## 5.4
```{r, echo=TRUE}
data5 <- data.frame(y,X)
lm.1 <-lm(log(y)~.,data5)
paste("The estimated effect size of each attribute is:")
for (i in 2:11)
{
  temp<- paste("beta", i-1,":", coef(lm.1)[i])
  (print(temp))
}

```

## 5.5
```{r}
vec_to_predict <-data.frame(1,1,1,1,1,1,1,1,1,1)
colnames(vec_to_predict) <- c("X1","X2","X3","X4","X5", "X6", "X7" ,"X8" ,"X9", "X10")
log_life_exp <- predict(lm.1,vec_to_predict)
excpted_life <- exp(log_life_exp)
```

The expected life predicted is: `r excpted_life`
